Recurrent Neural Networks for video object detection

### 2019-07-31 Paper/Paper_First_Draft.tex
Rework

\begin{abstract}
There is lot of scientific work about object detection in images. For many applications like for example autonomous driving the actual data on which classification has to be done are videos. This work compares different methods especially those which use Recurrent Neural Networks to detect objects in videos. We differ between feature-based methods, which feed feature maps of different frames into the recurrent units, box-level methods, which feed bounding boxes with class probabilities into the recurrent units and methods which use flow networks. This study indicates common outcomes of the compared methods like the benefit of including the temporal context into object detection and states conclusions and guidelines for video object detection networks. 
\end{abstract}

@@

First, we want to introduce feature-based Video Object Detection methods. As defined, for example, in [1-2] feature-based Video Object Detection methods fuse detectors which integrate features from multiple frames into their video detection. In most papers considered in this work this integration is done by recurrent units.

\subsection{Recurrent Multi-frame Single Shot Detector for Video Object Detection [1]}
Broad, Jones and Lee have in \cite{b1} and \cite{b12} the idea to design a multi-frame video object detector by inserting a fusion-layer into a classical Single Shot Detector (SSD) meta-architecture. Based on this idea they research in two main fields: On the one hand, they investigate different fusion methods and on the other hand they try several SSD meta-architectures [20-2.1.1; 20-3.6.1]. They test their approaches on the KITTI dataset \cite{b21} for autonomous driving and their model improves upon a state-of-the-art SSD model by 2.7 \% mAP. Finally they evaluate their best approach on Caltech Pedestrians Dataset \cite{b22} and find similar improvements of 5 \% in maP.   \newline

SSDs in general consist of two main components. First, an so called Feature Extractor, which gets as an input an image and outputs feature-maps. The other component is an Detection head which creates bounding boxes and class probabilities out of the feature maps. [1-3] Broad, Jones and Lee have the idea to insert a fusion layer in between those two components. As fusion techniques they test simple element-wise operations (e.g.: add or max), simple concatenations of features maps and recurrent layers [1-3]. Their experiments show that the recurrent layers perform best, because they add in contrast to the other two method new parameters to learn temporal context to the network. In addition, they observe that recurrent units do not slow down the computational speed significantly (only 5 fps slower then the baseline SSD) [1-4.1]. As a recurrent unit they use GRU because they observe that the results were similar to the results when they use LSTMs but the GRUs are faster to train [1-3.1.1]. Their final architecture is shown in Figure 1.

\begin{figure} [h]
\includegraphics[width=\columnwidth]{RMFSSD}
\caption{Architecture: Recurent Multi-frame single shot detector [1]. The Feature Extractor generates feature maps for four frames and feeds those feature maps into the GRUs. The Detection Head uses the final feature maps which are created by the GRU with respect to the temporal context to create Bounding Boxes and Class probabilities}
\end{figure}

In addition Broad, Jones and Lee test different types of SSDs as a baseline for their architecture. For all baseline SSDs the mAP was higher in comparison to the non-recurrent models. The mAP increase by 1.4 to 4.4 percent on KITTI dataset.  The best mAP is made with SqueezeDet+ \cite{b23} as a baseline SSD network [1-4.2].  \newline

Finally Broad, Jones and Lee use the Caltech Pedestrians dataset to expolore the effect of the number of prior frames and the frame-rate. They compare the single-frame SSD model, with the RMf-SSD using the prior frames and the RMf-SSD model using the frames t-2, t-4 and t-6. The improvement was 3 percentage points higher by using the frames t-2, t-4 and t-6 in comparison to use the prior 3 frames [1-4.4]. \newline

There is only a little information on the training of the Recurrent Multi-frame Single Shot Detector. They use the SequeezeDet Training strategies [23-3.3] and a pre-trained version of the baseline SSD. Finally, they use the SequezzeDet fine tuning strategy to train the whole network afterwards [12-2]. \newline

Overall Broad, Jones and Lee show three main things. First they show that including the temporal context improves single frame SSD methods. Moreover they show that Recurrent Units are a good approach to add the temporal context and finally they point that long time context (frames t-2, t-4, t-6) seems to be more important then short-term temporal context. Finally they reach an mAP of 83 \% on KITTI dataset [1-4.2] and a miss-rate of 29 \% on the Caltech Pedestrians dataset [1-4.1]. \newline

@@

\subsection{Mobile Video Object Detection with Temporally Aware Feature Maps [2]}
Liu and Zhu have in \cite{b2} the goal to design a video object detection architecture, which can run real-time (15 fps) on low-powered mobile and embedded devices. The key of their method is to combine convolutional layers with convolutional LSTMs. They investigate on the benefit from adding an LSTM into the baseline SSD, different types of Recurrent Layers (LSTM, GRU and bottleneck LSTMs), different dimensions of their bottleneck LSTMs and different LSTM placement strategies (Single LSTM placement and multiple LSTM placement). They test their model on Imagenet VID 2015 dataset \cite{b35} and reached a mAP of 54.4 \% while performing on 15 fps.  \newline

In the beginning they simply add one LSTM to their baseline SSDs architecture - MobileNet \cite{b24}. They observe that adding the LSTM improves the mAP in comparison to their baseline SSD architecture. Moreover, they investigate that the greatest improve is by adding the LSTM after the 13th convolutional Layer of the SSD. [2-4.2] \newline

Afterwards, they compare LSTMs, GRUs and Bottleneck LSTMs by placing them after the 13th convolutional layer. Bottleneck-LSTMs have been designed by Liu and Zhu to increase the efficiency of LSTMs. They use ReLU as activation function and feed Bottleneck feature map with less input channel then the original feature map into the LST. They come to the conclusion that Bottleneck-LSTMs are more effective the LSTMs and in the case of a convolutional kernel greater 1x1 even more effective than GRUs while attaining comparable perfomance. [2-3.4; 2-4.2]\newline

In addition to the bottleneck LSTMs Liu and Zhu extend their network with multipliers. They use $\alpha_{base}$, $\alpha_{ssd}$ and $\alpha_{lstm}$ as multiplier to scale the channel dimension of each layer. They find out that the accuracy of the model remains near constant up to $\alpha_{ssd}= 0.25 \alpha$. For the other multipliers they use the values: $\alpha_{base} = \alpha$ and $\alpha_{ssd} = 0.5 \alpha$. [2-3.3; 2-4.2] \newline

As shown in Fig. 2 the final model uses LSTMs after all feature maps, because Liu and Zhu observe that there is a slight performance improve by adding LSTMs after every feature map and nearly no change in computational cost [2-4.2].

\begin{figure} [h]
\includegraphics[width=\columnwidth]{Liu_Zhu}
\caption{Architecture Mobile Video Object Detection with temporally aware feature maps \cite{b2}. First 13 Convolutional Layeer create Feature Maps. Those Feature Maps are fed into the Bottleneck-LSTMs (faster LSTMs). Afterwards Convolutional-Layer create new Feature Maps and feed them again into Bottleneck-LSTMs.}
\end{figure}

@@

\subsection{Context Matters: Refining Object Detection in Video with Recurrent Neural Networks \cite{b4}}
In \cite{b4} Tripathi's, Lipton's, Belongie's and Nguyen's architecture consists two parts: A pseudo-labeler, which assigns labels to all video frames and a recurrent unit which refines those pseudo-labels by using the contextual information. Moreover, they describe a training strategy for their architecture and compare their approach to other models on the YouTube-Objects dataset (v2.0), which consists of the ten categories airplane, bird, boat, car, cow, dog, horse, mbike, train. Their model reaches an mAP of 68.73 percent which improves the strongest image-based baseline for Youtube-Video Objects dataset of 7.1\% [4-Abstract; 25]. \newline

The final architecture can be found in \textbf{Fig 10}. Tripathi, Lipton and Belongie first train a pretrained YOLO object detection network \cite{b20} as a  pseudo-labeler on the YouTube-Video Dataset. As specified in YOLO  they minimize the weighted squared detection loss and optimize classification and localization error simultaneously [4-3].

\begin{figure} [h]
\includegraphics[width=\columnwidth]{ContextMatters}
\caption{Architecture Context Matters: Refining Object Detection in Video with Recurrent Neural Networks \cite{b4}. First the "Pseudolabler" creates bounding boxes and class probabilities for every input frame. Afterwards the GRU fuses the output of the current and some past frames and refines the bounding boxes and class probabilities.}
\end{figure}

After training the pseudo-labeler they train the Recurrent Neural Network, which takes as an input the pseudo-labels and outputs improved prediction. The RNN consists of two GRU layers [4-2]. \newline

For training the whole network they use the following loss function to take both accuracy at the target frame and consistency of predictions across adjacent time steps into consideration. They choose the values of $\alpha = 0.2$, $\beta = 0.2$ and $\gamma = 0.1$ based on the detection performance on the validation set [4-2.1]: \newline

@@

Tripathi, Lipton, Belongie and Nguygen use the object detection loss ($d_{loss}$) as described in YOLO [26, 4-2.1.1]. The similarity loss ($s_{loss}$) considers the dissimilarity between the pseudo-labels and prediction at each frame t [4-2.1.2], the category loss ($c_{loss}$) takes wrong class probabilities into consideration [4-2.1.3] and the prediction-consistency loss ($pc_{loss}$) regularizes the model by encouraging smoothness predictions across the time-steps [4-2.1.4]. \newline

During the evaluation they find two possible areas of improvement for their approach. On the one hand the RNN is not able to recover from wrong predictions made by the pseudo-labeler after they have been fed into the RNN. This is a general disadvantage of box-level methods in comparison to feature-level methods. On the other hand, they observe that their network is not robust to motion [4-3.4]. \newline

Tripathi, Lipton, Belongie and Nguyen test their model on the Youtube-Objects dataset. Overall they outperform the best no-recurrent architecture (DA Yolo) in their comparison by 7\% mAP [4-3.1]. This again confirms the observatoin that adding recurrency to integrate temporal context improves the detection quality.  \newline

@@

\subsection{Spatially Supervised Recurrent Convolutional Neural Networks for Visual Object Tracking \cite{b5}}
Ning, Zhang, Huang, He, Ren and Wang design in \cite{b5} a combination of box-level and feature-level based Video detectors. They use the YOLO \cite{b27} network to create high-level visual features and preliminary location inferences and feed both into a recurrent unit. They test their approach on the OTB-30 dataset \cite{b28} and compared it with 9 different state-of-the-art trackers and outperform all of them. Their architecture, called ROLO, is shown in \textbf{figure}. [5-Abstract; 5-4]

@@

The architecture consists two main parts. The YOLO \cite{27} networks which collects visual features and outputs also preliminary location inferences and the LSTM which is used as a tracking module [5-2]. \newline

They use three phases to train their model: The pre-training phase of  convolutional layers for feature learning, the traditional YOLO training phase for object proposal and the LSTM training phase for object tracking. [5-3]  \newline

In the pre-training phase convolutional layers, which create feature maps are pretrained on ImageNet data. Afterwards the YOLO-architecture is adopted as detection module and trained by using the traditional YOLO training phase. Last they add LSTMs for tracking. The LSTMs are fed with, the feature representations from the convolutional layers, the Bounding boxes from the detection module and the output states from the LSTM in the previous time-step. For training they use the Mean Squared Error (MSE) [5-3]: \newline

@@

As an alternative, Ning, Zhang, Huang, He, Ren and Wang mention a Heatmap as  input for the LSTM. Therefor the prediction and the visual features are concatenated before adding them to the LSTM. This is helpful to visualize the intermediate results. [5-3.3] \newline

Special to this architecture is, that LSTM does regression in two folds. There is a regression within one frame between the location inferences and the high-level features and there is also regression over the different frames of the sequence by taking the temporal context into account [5-3.4].  \newline

In 2015 Wu, Lim and Yang published a comparison of different online object trackers on their one data set \cite{b28}. The best 9 architectures (STRUCK; CXT; OAB; CSK; VTD; VTS; LSK; TLD; RS) were used by Ning, Zhang, Huang, He, Ren and Wang to compare them with their own architecture. They use 30 videos with different objects (e.g.: car, human, Skater, Couple,..) out of the benchmark \cite{b28} dataset. They get the best tracking result in 13 videos and the second best in 3 videos. There is no other tracker that reaches the best results in more then 4 videos. \newline

@@

\subsection{Deep Feature Flow for Video Recognition \cite{2}}
Zhu, Xiong, Dai, Yuan and Wei develop in \cite{b2} a way to use flow nets to detect objects in video frames. As shown in figure 10 their architecture consists of three main parts: A network to create visual features, a network to create class probabilities and bounding boxes respectively the segmentation out of feature maps, and a network which estimates the optical flow. They tested their approach on the Cityscapes dataset with scenes for autonomous driving and ground-truth for semantic segmentation and the ImageNet VID dataset \cite{b35} with ground truth for object detection.

\begin{figure} [h]
\includegraphics[width=\columnwidth]{Flow}
\caption{Architecture Deep Feature Flow for Video Recognition}
\end{figure}

The paper differs between key frames and other frames. The network to create visual features $ N_{feat} $ only processes on key frames. It is a fully convolutional network, which takes as an input the image and outputs a feature maps. As a feature network they use a pretrained version of ResNet. \newline

The second network $ N_{task} $ does the recognition task over the feature maps. It performs on every frame.  Zhu, Xiong, Dai, Yuan and Wei use an R-FCN network for the recognition task.  \newline

For all non-key frames the feature maps are not constructed by the feature network. Instead, they are propagated by a flow network $ N_{flow} $.  Zhu, Xiong, Dai, Yuan and Wei use a state-of-the-art CNN based FlowNet architecture as a flow network. The flow estimation is given by: \newline

@@

$ f_{k} $ is the key frame's feature map, $ M_{i->k} $ is a two dimensional flow field, it projects back the location of an object in the current frame to the location in the key frame by using bilinear interpolation and  $ S_{i->k} $ is scale field. \newline

Zhu, Xiong, Dai, Yuan and Wei use a fixed key frame scheduling and they  see a potential improvement in changing the key frame policy. \newline

Overall Zhu, Xiong, Dai und Yuan show  a alternative  to recurrent neural networks to integrate the temporal context into the object tracking. They reach an mIoU up to 69.2 percent on Cityspace dataset and an mAP of 73.9 percent on ImageNet Vid. But those results are reached by processing with 5.6 and 4.05 fps. Both drop significantly with higher fps. Some recurrent papers in 2 and 3 reach higher mAPs on higher fps.

@@

The Flow-based approach \cite{3} has comparatively bad results on ImageNet. We only evaluated one flow-based paper, but the comparatively bad performance could be an evidence that flow-based approaches' benefit in comparison to recurrent approaches does not exist or is very small. \newline

@@

\bibitem{b11} Ian Goodfellow, Yoshua Bengio, Aaron Courville. Deep Learning (Adaptive Computation and Machine Learning). 2017.

@@

\vspace{12pt}
\end{thebibliography}
\end{document}

>>>>

\begin{abstract}
There is lots of scientific work about object detection in images. For many applications like for example autonomous driving the actual data on which classification has to be done are videos. This work compares different methods, especially those which use Recurrent Neural Networks to detect objects in videos. We differ between feature-based methods, which feed feature maps of different frames into the recurrent units, box-level methods, which feed bounding boxes with class probabilities into the recurrent units and methods which use flow networks. This study indicates common outcomes of the compared methods like the benefit of including the temporal context into object detection and states conclusions and guidelines for video object detection networks. 
\end{abstract}

@@

First, we want to introduce feature-based Video Object Detection methods. As defined, for example, in \cite{b1} feature-based Video Object Detection methods fuse detectors which integrate features from multiple frames into their video detection. In most papers considered in this work this integration is done by recurrent units.

\subsection{Recurrent Multi-frame Single Shot Detector for Video Object Detection \cite{b1}}
Broad, Jones and Lee have in \cite{b1} and \cite{b12} the idea to design a multi-frame video object detector by inserting a fusion-layer into a classical Single Shot Detector (SSD) meta-architecture. Based on this idea they research in two main fields: On the one hand, they investigate different fusion methods and on the other hand they try several SSD meta-architectures \cite{20}. They test their approaches on the KITTI dataset \cite{b21} for autonomous driving and their model improves upon a state-of-the-art SSD model by 2.7 \% mAP. Finally they evaluate their best approach on Caltech Pedestrians Dataset \cite{b22} and find similar improvements of 5 \% in maP.   \newline

SSDs in general consist of two main components. First, an so called Feature Extractor, which gets as an input an image and outputs feature-maps. The other component is an Detection head which creates bounding boxes and class probabilities out of the feature maps \cite{1}. Broad, Jones and Lee have the idea to insert a fusion layer in between those two components. As fusion techniques they test simple element-wise operations (e.g.: add or max), simple concatenations of features maps and recurrent layers \cite{1}. Their experiments show that the recurrent layers perform best, because they add in contrast to the other two method new parameters to learn temporal context to the network. In addition, they observe that recurrent units do not slow down the computational speed significantly (only 5 fps slower then the baseline SSD) \cite{1}. As a recurrent unit they use GRU because they observe that the results were similar to the results when they use LSTMs but the GRUs are faster to train \cite{1}. Their final architecture is shown in Figure 1.

\begin{figure} [h]
\includegraphics[width=\columnwidth]{RMFSSD}
\caption{Architecture: Recurent Multi-frame single shot detector \cite{b1}. The Feature Extractor generates feature maps for four frames and feeds those feature maps into the GRUs (Gated Recurrent Units). The Detection Head uses the final feature maps which are created by the GRU with respect to the temporal context to create Bounding Boxes and Class probabilities}
\end{figure}

In addition Broad, Jones and Lee test different types of SSDs as a baseline for their architecture. For all baseline SSDs the mAP was higher in comparison to the non-recurrent models. The mAP increase by 1.4 to 4.4 percent on KITTI dataset.  The best mAP is achieved using SqueezeDet+ \cite{b23} as a baseline SSD network \cite{b1}.  \newline

Finally Broad, Jones and Lee use the Caltech Pedestrians dataset to expolore the effect of the number of prior frames and the frame-rate. They compare the single-frame SSD model, with the RMf-SSD using the prior frames and the RMf-SSD model using the frames t-2, t-4 and t-6. The improvement was 3 percentage points higher by using the frames t-2, t-4 and t-6 in comparison to use the prior 3 frames \cite{b1}. \newline

There is only a little information on the training of the Recurrent Multi-frame Single Shot Detector. They use the SequeezeDet Training strategies \cite{b23} and a pre-trained version of the baseline SSD. Finally, they use the SequezzeDet fine tuning strategy to train the whole network afterwards \cite{b12}. \newline

Overall Broad, Jones and Lee show three main things. First they show that including the temporal context improves single frame SSD methods. Moreover they show that Recurrent Units are a good approach to add the temporal context and finally they point that long time context (frames t-2, t-4, t-6) seems to be more important then short-term temporal context. Finally they reach an mAP of 83 \% on KITTI dataset and a miss-rate of 29 \% on the Caltech Pedestrians dataset \cite{b1}. \newline

@@

\subsection{Mobile Video Object Detection with Temporally Aware Feature Maps \cite{b2}}
Liu and Zhu have in \cite{b2} the goal to design a video object detection architecture, which can run real-time (15 fps) on low-powered mobile and embedded devices. The key of their method is to combine convolutional layers with convolutional LSTMs. They investigate on the benefit from adding an LSTM into the baseline SSD, different types of Recurrent Layers (LSTM, GRU and bottleneck LSTMs), different dimensions of their bottleneck LSTMs and different LSTM placement strategies (Single LSTM placement and multiple LSTM placement). They test their model on Imagenet VID 2015 dataset \cite{b35} and reached a mAP of 54.4 \% while performing on 15 fps.  \newline

In the beginning they simply add one LSTM to their baseline SSDs architecture - MobileNet \cite{b24}. They observe that adding the LSTM improves the mAP in comparison to their baseline SSD architecture. Moreover, they investigate that the greatest improve is by adding the LSTM after the 13th convolutional Layer of the SSD \cite{b2}. \newline

Afterwards, they compare LSTMs, GRUs and Bottleneck LSTMs by placing them after the 13th convolutional layer. Bottleneck-LSTMs have been designed by Liu and Zhu to increase the efficiency of LSTMs. They use convolutions with ReLU as activation function and feed Bottleneck feature map with less input channel then the original feature map into the LST. They come to the conclusion that Bottleneck-LSTMs are more effective the LSTMs and in the case of a convolutional kernel greater 1x1 even more effective than GRUs while attaining comparable perfomance. \cite{b2} \newline

In addition to the bottleneck LSTMs Liu and Zhu extend their network with multipliers. They use $\alpha_{base}$, $\alpha_{ssd}$ and $\alpha_{lstm}$ as multiplier to scale the channel dimension of each layer. They find out that the accuracy of the model remains near constant up to $\alpha_{ssd}= 0.25 \alpha$. For the other multipliers they use the values: $\alpha_{base} = \alpha$ and $\alpha_{ssd} = 0.5 \alpha$. \cite{b2} \newline

As shown in Fig. 2 the final model uses LSTMs after each convolutional Layer, because Liu and Zhu observe that there is a slight performance improve by adding LSTMs after every feature map and nearly no change in computational cost \cite{b2}.

\begin{figure} [h]
\includegraphics[width=\columnwidth]{Liu_Zhu}
\caption{Architecture Mobile Video Object Detection with temporally aware feature maps \cite{b2}. First 13 Convolutional Layeer create Feature Maps. Those Feature Maps are fed into the convolutional Bottleneck-LSTMs (faster LSTMs which use convolutions). Afterwards Convolutional-Layer create new Feature Maps and feed them again into Bottleneck-LSTMs.}
\end{figure}

@@

\subsection{Context Matters: Refining Object Detection in Video with Recurrent Neural Networks \cite{b4}}
In \cite{b4} Tripathi's, Lipton's, Belongie's and Nguyen's architecture consists two parts: A pseudo-labeler, which assigns labels to all video frames and a recurrent unit which refines those pseudo-labels by using the contextual information. Moreover, they describe a training strategy for their architecture and compare their approach to other models on the YouTube-Objects dataset (v2.0) \cite{b25} , which consists of the ten categories airplane, bird, boat, car, cow, dog, horse, mbike, train. Their model reaches an mAP of 68.73 percent which improves the strongest image-based baseline for Youtube-Video Objects dataset of 7.1\% \cite{b4}. \newline

The final architecture can be found in \textbf{Fig 10}. Tripathi, Lipton and Belongie first train a pretrained YOLO object detection network \cite{b20} as a  pseudo-labeler on the YouTube-Video Dataset. As specified in YOLO  they minimize the weighted squared detection loss and optimize classification and localization error simultaneously \cite{b4}.

\begin{figure} [h]
\includegraphics[width=\columnwidth]{ContextMatters}
\caption{Architecture Context Matters: Refining Object Detection in Video with Recurrent Neural Networks \cite{b4}. First the "Pseudolabler" creates bounding boxes and class probabilities for every input frame. Afterwards the GRU (Gated Recurrent Unit) fuses the output of the current and some past frames and refines the bounding boxes and class probabilities.}
\end{figure}

After training the pseudo-labeler they train the Recurrent Neural Network, which takes as an input the pseudo-labels and outputs improved prediction. The RNN consists of two GRU layers \cite{b4}. \newline

For training the whole network they use the following loss function to take both accuracy at the target frame and consistency of predictions across adjacent time steps into consideration. They choose the values of $\alpha = 0.2$, $\beta = 0.2$ and $\gamma = 0.1$ based on the detection performance on the validation set \cite{b4}: \newline

@@

Tripathi, Lipton, Belongie and Nguygen use the object detection loss ($d_{loss}$) as described in YOLO \cite{b26} \cite{b4}. The similarity loss ($s_{loss}$) considers the dissimilarity between the pseudo-labels and prediction at each frame t, the category loss ($c_{loss}$) takes wrong class probabilities into consideration and the prediction-consistency loss ($pc_{loss}$) regularizes the model by encouraging smoothness predictions across the time-steps \cite{b4}. \newline

During the evaluation they find two possible areas of improvement for their approach. On the one hand the RNN is not able to recover from wrong predictions made by the pseudo-labeler after they have been fed into the RNN. This is a general disadvantage of box-level methods in comparison to feature-level methods. On the other hand, they observe that their network is not robust to motion \cite{b4}. \newline

Tripathi, Lipton, Belongie and Nguyen test their model on the Youtube-Objects dataset. Overall they outperform the best no-recurrent architecture (DA Yolo) in their comparison by 7\% mAP \cite{b4}. This again confirms the observatoin that adding recurrency to integrate temporal context improves the detection quality.  \newline

@@

\subsection{Spatially Supervised Recurrent Convolutional Neural Networks for Visual Object Tracking \cite{b5}}
Ning, Zhang, Huang, He, Ren and Wang design in \cite{b5} a combination of box-level and feature-level based Video detectors. They use the YOLO \cite{b26} network to create high-level visual features and preliminary location inferences and feed both into a recurrent unit. They test their approach on the OTB-30 dataset \cite{b28} and compared it with 9 different state-of-the-art trackers and outperform all of them. Their architecture, called ROLO, is shown in figure 11.  \cite{b5}

@@

The architecture consists two main parts. The YOLO \cite{b26} networks which collects visual features and outputs also preliminary location inferences and the LSTM which is used as a tracking module \cite{b5}. \newline

They use three phases to train their model: The pre-training phase of  convolutional layers for feature learning, the traditional YOLO training phase for object proposal and the LSTM training phase for object tracking \cite{b5}.  \newline

In the pre-training phase convolutional layers, which create feature maps are pretrained on ImageNet data. Afterwards the YOLO-architecture is adopted as detection module and trained by using the traditional YOLO training phase. Lastly they add LSTMs for tracking. The LSTMs are fed with, the feature representations from the convolutional layers, the Bounding boxes from the detection module and the output states from the LSTM in the previous time-step. For training they use the Mean Squared Error (MSE) \cite{b5}: \newline

@@

As an alternative, Ning, Zhang, Huang, He, Ren and Wang mention a Heatmap as  input for the LSTM. Therefor the prediction and the visual features are concatenated before adding them to the LSTM. This is helpful to visualize the intermediate results \cite{b5}. \newline

Special to this architecture is, that LSTM does regression in two folds. There is a regression within one frame between the location inferences and the high-level features and there is also regression over the different frames of the sequence by taking the temporal context into account \cite{b5}.  \newline

In 2015 Wu, Lim and Yang published a comparison of different online object trackers on their one data set \cite{b28}. The best 9 architectures (STRUCK \cite{b47}; CXT \cite{b48}; OAB \cite{b49}; CSK \cite{b50}; VTD \cite{b51}; VTS \cite{b52}; LSK \cite{b53}; TLD \cite{b54}; RS \cite{b55}) were used by Ning, Zhang, Huang, He, Ren and Wang to compare them with their own architecture. They use 30 videos with different objects (e.g.: car, human, Skater, Couple,..) out of the benchmark \cite{b28} dataset. They get the best tracking result in 13 videos and the second best in 3 videos. There is no other tracker that reaches the best results in more then 4 videos. \newline

@@

\subsection{Deep Feature Flow for Video Recognition \cite{b3}}
Zhu, Xiong, Dai, Yuan and Wei develop in \cite{b3} a way to use flow nets to detect objects in video frames. As shown in figure 10 their architecture consists of three main parts: A network to create visual features, a network to create class probabilities and bounding boxes respectively the segmentation out of feature maps, and a network which estimates the optical flow. They tested their approach on the Cityscapes dataset \cite{b56}  with scenes for autonomous driving and ground-truth for semantic segmentation and the ImageNet VID dataset \cite{b35} with ground truth for object detection.

\begin{figure} [h]
\includegraphics[width=\columnwidth]{Flow}
\caption{Architecture Deep Feature Flow for Video Recognition \cite{b3}. The feature Network $N_{feat}$ extracts visual features for the key frames. The $N_{task}$ networks uses visual features to create Bounding boxes and Class probabilities. For non-key frame images, the flow networks F estimates the feature maps based on in a image sequence.}
\end{figure}

The paper differs between key frames and other frames. The network to create visual features $ N_{feat} $ only processes on key frames. It is a fully convolutional network, which takes as an input the image and outputs a feature maps. As a feature network they use a pretrained version of ResNet \cite{b40}, \cite{b3}. \newline

The second network $ N_{task} $ does the recognition task over the feature maps. It performs on every frame.  Zhu, Xiong, Dai, Yuan and Wei use an R-FCN \cite{b19} network for the recognition task. \cite{b3}  \newline

For all non-key frames the feature maps are not constructed by the feature network. Instead, they are propagated by a flow network $ N_{flow} $.  Zhu, Xiong, Dai, Yuan and Wei use a state-of-the-art CNN based FlowNet architecture \cite{b57} as a flow network. The flow estimation is given by \cite{b3} \newline

@@

$ f_{k} $ is the key frame's feature map, $ M_{i->k} $ is a two dimensional flow field, it projects back the location of an object in the current frame to the location in the key frame by using bilinear interpolation and  $ S_{i->k} $ is scale field \cite{b3}. \newline

Zhu, Xiong, Dai, Yuan and Wei use a fixed key frame scheduling and they  see a potential improvement in changing the key frame policy \cite{b3}. \newline

Overall Zhu, Xiong, Dai und Yuan show  a alternative  to recurrent neural networks to integrate the temporal context into the object tracking. They reach an mIoU up to 69.2 percent on Cityspace dataset and an mAP of 73.9 percent on ImageNet Vid. But those results are reached by processing with 5.6 and 4.05 fps. Both drop significantly with higher fps. Some recurrent papers in 2 and 3 reach higher mAPs on higher fps \cite{b3}.

@@

The Flow-based approach \cite{b3} has comparatively bad results on ImageNet. We only evaluated one flow-based paper, but the comparatively bad performance could be an evidence that flow-based approaches' benefit in comparison to recurrent approaches does not exist or is very small. \newline

@@

\bibitem{b11} Ian Goodfellow, Yoshua Bengio, Aaron Courville. Deep Learning (Adaptive Computation and Machine Learning) , \textit{Chapter 10}. 2017.

@@

\bibitem{b47} S. Hare, S. Golodetz, A. Saffari, V. Vineet, M. M. Cheng, S. Hicks, P. Torr. Struck: Structured output tracking with kernels. \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence, PP(99):1-1, 2105}
\bibitem{b48} Thang Ba Dinh, Nam Vo, Gérard Medioni. Context tracker: Exploring supporters and distracters in unconstrained environments, In CVPR, pages 1177-1184. IEEE, 2011.
\bibitem{b49} Helmut Grabner, Michael Grabner, Horst Bischof. Real-time tracking via on-line boosting. In BMVC volume 1, page 6, 2006.
\bibitem{b50} Joao F Henriques, Rui Cuisero, Pedro Martins, Jorge Batista. Exploiting the circulant structure of tracking-by-detection with kernels. In \textit{ECCV}, pages 702-715. Springer 2012.
\bibitem{b51} Junseok Kwon, Kyoung Mu Lee. Visual tracking decomposition. In \textit{CVPR}, pages 1269-1276. IEEE, 2010.
\bibitem{b52} Junseok Kwon, Kyoung Mu Lee. Tracking by sampling trackers. In \textit{ICCV}, pages 1195-1202. IEEE, 2011.
\bibitem{b53} Baiyan Liu, Junzhou Huang, Lin Yang, Casimir Kulikowsk. Robust tracking using local sparse appearance model and k-selection. In \textit{CVPR}, pages 1313-1320. IEEE, 2011.
\bibitem{b54} Zdenek Kalal, Juri Matas, Krystian Mikolajcyk. Pn learning: Bootstrapping binary classifiers by structural constrains. In \textit{CVPR}, pages 49-56. IEEE, 2010.
\bibitem{b55} Robert T Collins, Yanxi Liu, Marius Leordeanu. Online selection of discriminative tracking features. \textit{Pattern Analysis and Machine Intelligence, IEEE Transactions on} 27(10): 1631-1643, 2005.
\bibitem{b56} M. Cordts, M. Omran, S. Ramos, T. Rehfeld, M. Enzweiler, R. Benenson, U. Franke, S. Roth, B. Schiele. The cityspaces dataset for semantic urban scene understanding. In \textit{CVPR}, 2016.
\bibitem{b57} A. Dosovitskiy, P. Fischer, E. Ilg, P. Hauser, C. Hazirbas, V. Golkov. Flownet: Learning optical flow with convolutional networks. In \textit{ICCV}, 2015.

\vspace{12pt}
\end{thebibliography}
\end{document}
